---
title: "GG606 - Assignment 1"
author: "Student Name"
date: "`r paste(format(Sys.Date(), '%Y-%m-%d'))`"
output: html_document
---


## Assignment 1 - Importing, parsing, and querying data in the wild

1. Read the data in and clean it for analysis, used the `readr` package functions for reading and parsing data. \[5 marks\]

My answer is written here and is explains what I did and why.

```{r echo=TRUE}
#code 
#***********************************
library(readr)


```

2. Did more earthquakes happen on weekends or weekdays? \[5 marks\]
```{r echo=TRUE}
#code 
#***********************************



```
The above analysis demonstrates...


3. Has there been any change in the frequency of earthquakes? \[5 marks\]
```{r echo=TRUE}
#code 
#***********************************



```
The above analysis demonstrates...


4. Where were there more earthquakes in the 1980s, South America or North America? \[5 marks\]
```{r echo=TRUE}
#code 
#***********************************



```
The above analysis demonstrates...


5. Has there been any geographic shifts in the distribution of earthquakes? \[10 marks\]
```{r echo=TRUE}
#code 
#***********************************



```
The above analysis demonstrates...


